lfl: An \R{} Package for Linguistic Fuzzy Logic

### 2021-06-09 article.tex
Updates from Overleaf

The second case study will work with the famous Iris dataset \citep{iris1, iris2}:

>>>>

The second case study will work with the famous Iris dataset \citep{iris1, iris2}, which is also available in \R{} as a built-in data frame:
%
\input{chunks/chunk-casestudy-assoc-iris}
%
We are going to search for association rules in that database: first by using the \lfl{} package and next with the \pkg{arules} package. After that, we will compare the results.

First of all, we transform the \texttt{iris} data frame into fuzzy sets.
%
\input{chunks/chunk-casestudy-assoc-lcut}
%
This creates a data frame with each column representing linguistic expressions on original Iris data attributes.

We can search for association rules, convert the result into a \texttt{data.frame} and print first 6 rules as follows:
%
\input{chunks/chunk-casestudy-assoc-searchrules}
%

\input{chunks/chunk-casestudy-assoc-reduce}
